---
title: "Steak Preferences in the United States"
subtitle: "Summary Report For the `r params$region` Region"
author: "Hongchen Xiao"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    logo: images/sunstar.png
params:
  region: 
    label: "Region:"
    value: Mountain
    input: select
    choices: ["East North Central","East South Central", 
              "Middle Atlantic","Mountain", "New England", 
              "Pacific","South Atlantic", "West North Central",
              "West South Central"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE }
knitr::read_chunk("code/setup.R")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r loadData}
```



```{r child= "text/backgroundSection.Rmd"}

```

```{r child= "text/purposeSection.Rmd"}

```


## Demographic Summary Tables

The age categories of the `r nrow(sdat)` survey
respondents were:

```{r}
# create table of the age categories
tb <- sdat %>%
  select(age) %>%
  table() %>%
  prop.table()*100

# convert table to data frame
dt <- as.data.frame(tb)

# use kable from knitr package to make table
# and use kable styling from kableExtra package
knitr::kable(dt, format="html",
             col.names=c("Ages","%"),
             digits=2,
             caption="Ages of Survey Respondents") %>%
  kableExtra::kable_styling(bootstrap_options ="striped",
                            full_width=FALSE)
```

The education levels of the `r nrow(sdat)` survey respondents were:

```{r}
# repeat for education
tb <-sdat %>% 
  select(educ) %>%
  table() %>%
  prop.table()*100

dt <-as.data.frame(tb)

knitr::kable(dt, format="html",
             col.names=c("Education","%"),
             digits=2,
             caption="Education of Survey Respondents") %>%
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width=FALSE)
```


The income levels of the `r nrow(sdat)` survey respondents were:

```{r}
# repeat for household income
tb <-sdat %>% 
  select(hhold_income) %>%
  table() %>%
  prop.table()*100

dt <-as.data.frame(tb)

knitr::kable(dt, format="html",
             col.names=c("Income","%"),
             digits=2,
             caption="Income of Survey Respondents") %>%
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width=FALSE)
```


## _OPTIONAL_ Demographics of Survey Respondents in a Merged Table

This section is provided as an example of how to merge the three demographic summary tables for the `r nrow(sdat)` survey respondents above into a single merged table.

```{r makeTable, code=readLines("code/makeTable.R")}
```

## Steak Preparation Preference by Gender

Finally, here is a breakdown of the `r nrow(sdat)` survey respondents for the `r params$region` region of the US on how they prefer their steak to be prepared by gender.

```{r}
knitr::read_chunk("code/makeChart.R")
```
```{r makeCharts}

```









